Two Problems for Sophistication

### 2015-01-21 Facticity/Facticity/paper.tex
...

A \emph{model class} is a set of model indices. We distinguish four important model classes: 
\begin{enumerate}
\item $\C=\N$, the indices of all partial computable functions
\item $\T=\{i:\tn{$\phi_i$ is total}\}$. Note that $\T$ is not enumerable.
\item $\K$ is an enumerable set such that $\{\phi_i:i\in\K\}$ is the set of all partial computable prefix functions
\item $\F$ is an enumerable set such that $\{\phi_i:i\in\F\}$ contains a uniform code for every finite set. A uniform code for a finite set $S$ is a total computable surjective function $f:\{0,1\}^{\lceil|S|\rceil}\to S$.
\end{enumerate}

We sometimes need to map binary strings to a prefix-free set. We denote by $\bar x$ the prefix-encoded representation for $x$. We require that the mapping satisfies $|\bar{x}| = |x|+O(\log(|x|)$ (see eg. \cite[Section~1.4]{li1993introduction}). To simplify notation, we will sometimes conflate natural numbers and binary strings, implicitly using the ordering $(0, \epsilon)$, $(1, 0)$, $(2, 1)$, $(3, 00)$, $(4, 01)$, \ldots

Now define the Kolmogorov complexity of a binary string $x$, with respect to a model class $\M$ and a numbering $\psi$, as follows:
\[
C^{\M,\psi}(x)=\min\{\bar\imath y:\psi_i(y)=x,i\in\M\}.
\]
The model class $\C$ gives us the plain Kolmogorov complexity and the $\K$ gives us the prefix-free Kolmogorov complexity. The complexity is invariant to the numbering for these model classes, so we may omit it from the superscript.

@@

In these works, no constraints are placed on the used numbering. This makes these approaches vulnerable to the so-called \emph{nickname problem}: the number of bits required to specify a model becomes very dependent on the numbering. This problem is severe: \emph{any} index sophistication without requirements on the numbering is either bounded, or not invariant:

>>>>

A \emph{model class} is a set of model indices. We distinguish four important model classes: 
\begin{enumerate}
\item $\C=\N$, the indices of all partial computable functions
\item $\T=\{i:\tn{$\phi_i$ is total}\}$. Note that $\T$ is not computably enumerable.
\item $\K$ is an enumerable set such that $\{\phi_i:i\in\K\}$ is the set of all partial computable prefix functions
\item $\F$ is an enumerable set such that $\{\phi_i:i\in\F\}$ contains a uniform code for every finite set. A uniform code for a finite set $S$ is a total computable surjective function $f:\{0,1\}^{\lceil|S|\rceil}\to S$.
\end{enumerate}
We sometimes need to map binary strings to a prefix-free set. We denote by $\br{x}$ the prefix-encoded representation for $x$. We require that the mapping satisfies $|\br{x}| = |x|+O(\log(|x|)$ (see eg. \cite[Section~1.4]{li1993introduction}). To simplify notation, we will sometimes conflate natural numbers and binary strings, implicitly using the ordering $(0, \epsilon)$, $(1, 0)$, $(2, 1)$, $(3, 00)$, $(4, 01)$, \ldots

Now define the Kolmogorov complexity of a binary string $x$, with respect to a model class $\M$ and a numbering $\psi$, as follows:
\[
C^{\M,\psi}(x)=\min\{\bar\imath y:\psi_i(y)=x,i\in\M\}.
\]
The model class $\C$ gives us the plain Kolmogorov complexity and $\K$ gives us the prefix-free Kolmogorov complexity. For $\C$ and $\K$, the complexity is invariant to the numbering, so we may omit it from the superscript.

@@

In these works, no constraints are placed on the numbering. This makes these approaches vulnerable to the so-called \emph{nickname problem}: the number of bits required to specify a model becomes very dependent on the numbering. This problem is severe: \emph{any} index sophistication without requirements on the numbering is either bounded, or not invariant:
